Latentcor: An R Package for Latent Correlation Estimation

### 2021-06-05 paper/paper.Rmd
Commit

# Data generation
simdata <- GenerateData(n=n, trueidx1 = trueidx1, trueidx2 = trueidx2,
                        maxcancor = maxcancor,
                        Sigma1 = Sigma1, Sigma2 = Sigma2,
                        copula1 = "exp", copula2 = "cube",
                        muZ = mu,
                        type1 = "binary", type2 = "continuous",
                        c1 = rep(1, p1), c2 =  NULL
)
X1 <- simdata$X1; X2 <- simdata$X2; Sigma12_tt <- simdata$Sigma12
# Estimate latent correlation matrix with original method
R1_b_org <- estR(X1, "binary", method = "original")
R2_c_org <- estR(X2, "continuous", method = "original")
R12_bc_org <- estR(X1, type1 = "binary", X2, type2 = "continuous",
                              method = "original")$R12
# Estimate latent correlation matrix with original method
R1_b_approx <- estR(X1, "binary", method = "approx")
R2_c_approx <- estR(X2, "continuous", method = "approx")
R12_bc_approx <- estR(X1, type1 = "binary", X2, type2 = "continuous",
                              method = "approx")$R12
```

>>>>

# Data generation
simdata <- GenerateData(n=n, trueidx1 = trueidx1, trueidx2 = trueidx2,
                        maxcancor = maxcancor,
                        Sigma1 = Sigma1, Sigma2 = Sigma2,
                        copula1 = "exp", copula2 = "cube",
                        muZ = mu,
                        type1 = "binary", type2 = "continuous",
                        c1 = rep(1, p1), c2 =  NULL
)
X1 <- simdata$X1; X2 <- simdata$X2; Sigma12_tt <- simdata$Sigma12
# Estimate latent correlation matrix with original method
R1_tt_org <- estR(X1, "binary", method = "original")
R2_tt_org <- estR(X2, "continuous", method = "original")
R12_tt_org <- estR(X1, type1 = "binary", X2, type2 = "continuous",
                              method = "original")$R12
# Estimate latent correlation matrix with original method
R1_tt_org <- estR(X1, "binary", method = "approx")
R2_tt_org <- estR(X2, "continuous", method = "approx")
R12_tt_org <- estR(X1, type1 = "binary", X2, type2 = "continuous",
                              method = "approx")$R12
```

### 2021-06-05 paper/paper.tex
Commit

% --- Header / Footer ---------------------------------------------------------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
%\renewcommand{\headrulewidth}{0.50pt}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[L]{\hspace{-0.75cm}\includegraphics[width=5.5cm]{C:/Users/sharkmanhmz/Documents/R/R-4.1.0/library/rticles/rmarkdown/templates/joss/resources/JOSS-logo.png}}
\fancyhead[C]{}
\fancyhead[R]{}
\renewcommand{\footrulewidth}{0.25pt}

@@

% Pandoc citation processing
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for calculating minipage widths
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

Currently there is no standalone package dealing with latent correlation
for mixed data type like we did in \emph{latentcor}. The R package
\emph{stats} (Team \& others, 2013) have some functionality to calculate
different type of correlations (Pearson, Kendall and Spearman). The R
package \emph{pcaPP} (Croux, Filzmoser, \& Fritz, 2013) provides a fast
calculation for Kendall's \tau. The R package \emph{MixedCCA} (Yoon,
Carroll, \& Gaynanova, 2020) have functionality for latent correlation
estimation as an intermediate step for canonical correlation analysis on
mixed data. No package deal with latent correlation across mixed data
type.

>>>>

% --- Header / Footer ---------------------------------------------------------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
%\renewcommand{\headrulewidth}{0.50pt}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[L]{\hspace{-0.75cm}\includegraphics[width=5.5cm]{C:/Users/mingz/OneDrive/Documents/R/win-library/4.1/rticles/rmarkdown/templates/joss/resources/JOSS-logo.png}}
\fancyhead[C]{}
\fancyhead[R]{}
\renewcommand{\footrulewidth}{0.25pt}

@@

% Pandoc citation processing
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
% for Pandoc 2.8 to 2.10.1
\newenvironment{cslreferences}%
  {}%
  {\par}
% For Pandoc 2.11+
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc} % for calculating minipage widths
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

Currently there is no standalone package dealing with latent correlation
for mixed data type like we did in \emph{latentcor}. The R package
\emph{stats} (Team \& others, 2013) have some functionality to calculate
different type of correlations (Pearson, Kendall and Spearman). The R
package \emph{pcaPP} (Croux, Filzmoser, \& Fritz, 2013) provides a fast
calculation for Kendall's \(\tau\). The R package \emph{MixedCCA} (Yoon,
Carroll, \& Gaynanova, 2020) have functionality for latent correlation
estimation as an intermediate step for canonical correlation analysis on
mixed data. No package deal with latent correlation across mixed data
type.
